\begin{justify}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection[page2sidebar]{Projects}

%%%%%%%%%%%%%
%Project 1
%%%%%%%%%%%%%

\cvproject{\href{https://github.com/atulvidyarthi29/haven}{Haven - A Crime Tipping and Reporting Portal}}

\begin{itemize}
    \item Working on an online forum for people to help or seek help from others anonymously. Target audience are people who are victims or convicts in civil or criminal cases. 
    \item Users can also report any criminal activity in the locality directly to the authorities. There are journalists to verify these posts.
    \item Added speech to text converter and language translator for effective communication.
    \item Spring boot is being used for the microservices architectural design.
\end{itemize}
\medskip
% \divider

%%%%%%%%%%%%%
%Project 2
%%%%%%%%%%%%%

\cvproject{\href{https://github.com/atulvidyarthi29/Kudabin}{KudaBin - A Waste Management App}}

\begin{itemize}
    \item Developed a mobile app for sewage collection to manage collection centers, collection agents, collection vehicles and customers.
    \item Requesters can track collection vehicles on Google Map who, on successful pick-up, can also submit feedback. Lastly, the users can report places where garbage is dumped illegally.
    
  \item Flutter is used for the mobile app along with various google map libraries and NodeJs for backend. For live tracking, firebase is used.

\end{itemize}
\medskip
% \divider
%%%%%%%%%%%%%
%Project 3
%%%%%%%%%%%%%

\cvproject{\href{https://github.com/atulvidyarthi29/BlueTech}{BlueTech ERP - An Enterprise Resource Planning Software}}

\begin{itemize}
  \item Developed a centralized business management software for Sales, HR and Finance department. Recruitment could be done through a link sent on the registered email address.
  \item  Payment gateway was also integrated to let any company buy this software.  The whole application was built using Django.
\end{itemize}
% \medskip
\medskip
% \divider

%%%%%%%%%%%%%
%Project 4
%%%%%%%%%%%%%

\cvproject{\href{https://github.com/atulvidyarthi29/Carpool}{Carpool - A Car Rental Website}}

\begin{itemize}
  \item Developed a serverless Flask application using AWS services like Amazon Cognito, DynamoDB, CloudFront, Amazon Lambda, Amazon Lex, S3 bucket and AWS IAM and deployed it using Zappa.
\end{itemize}
% \medskip
\medskip
% \divider

%%%%%%%%%%%%%
%Project 6
%%%%%%%%%%%%%

\cvproject{\href{https://github.com/atulvidyarthi29/Digital-College}{Digital College - A Learning Management System}}

\begin{itemize}
  \item Developed a Django application with materialized CSS for UI to serve as a platform for student-teacher interaction, club-related activities, student progress, assignment submission, course planning, quiz conduction and forum.
\end{itemize}
\medskip
% \medskip
% \divider

%%%%%%%%%%%%%
%Project 5
%%%%%%%%%%%%%

\cvproject{\href{https://github.com/atulvidyarthi29/Echo}{Echo - A Music Player}}

\begin{itemize}
  \item Developed a Kotlin App which can play songs from the device with shake-to-change the song feature and a cool visualizer.
\end{itemize}
\medskip
% \divider


%%%%%%%%%%%%%
%Project 7
%%%%%%%%%%%%%

% \href{https://github.com/atulvidyarthi29}{Other works on Github}


% \cvsection[page2sidebar]{Achievements}

% \begin{itemize}
%     \item \href{https://www.coursera.org/account/accomplishments/certificate/EAHYMWXEXJ7U}{Greedy Algorithms, Minimum Spanning Trees, and Dynamic Programming on Coursera}
%     \item \href{https://www.dropbox.com/s/6l245ql0brkzeyx/Android%20App%20Development%20Training%20-%20Certificate%20of%20Completion.pdf?dl=0}{Android App Development on Internshala}
% \end{itemize}

\cvsection[page2sidebar]{Certifications}

\begin{itemize}
    \item \href{https://www.coursera.org/account/accomplishments/certificate/EAHYMWXEXJ7U}{Greedy Algorithms, Minimum Spanning Trees, and Dynamic Programming on Coursera}
    \item \href{https://www.dropbox.com/s/6l245ql0brkzeyx/Android%20App%20Development%20Training%20-%20Certificate%20of%20Completion.pdf?dl=0}{Android App Development on Internshala}
\end{itemize}

\end{justify}